### 2009-11-29 doc/manuals/janitor/tex_titlepage/titlepage.tex
Update of Michael's email address.
Merged tex_titlepage/titlepage.tex in manuals/janitor/ and tech_doc/janitor/

%%%%---- The title ----
{\centering \textsc{\Large Dynamic Runtime Environments with Janitor}
\\\vspace{1cm} \normalsize\textcolor{discreeturgent}{This document is still under development, but don't hesitate sending your comments and suggestions to moeller@inb.uni-luebeck.de.} % DELETE ONLY THAT LINE!!!
\Large \par}
\vspace*{0.5cm}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large Michael Glodek\footnote{glodek@inb.uni-luebeck.de}, Daniel Bayer,  Steffen M\"oller\footnote{moeller@inb.uni-luebeck.de} \par}

>>>>

%%%%---- The title ----
{\centering \textsc{\Large Dynamic Runtime Environments with Janitor}
\\\vspace{1cm} \normalsize\textcolor{discreeturgent}{This
	Janitor and this document with it is under continuous development.
	Your comments and suggestions are appreciated.} % DELETE ONLY THAT LINE!!!
\Large \par}
\vspace*{0.5cm}

@@

\vspace*{1.5cm}
%%%%---- A list of authors ----
    {\centering \large Michael Glodek, Daniel Bayer,  Steffen M\"oller\footnote{moeller@inb.uni-luebeck.de} \par}
